Trends in Atomistic Simulation Software Usage [Article v\versionnumber]

### 2021-10-24 manuscript.tex
add package 'url' to facilitate wrapping URLs at hyphenation; remove section numbering for sections after main text
fix title for publication

@@

\newcommand{\versionnumber}{1.3}  % you should update the minor version number in preprints and major version number of submissions.
\newcommand{\githubrepository}{\url{https://github.com/ltalirz/livecoms-atomistic-software}}  %this should be the main github repository for this article

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% ARTICLE SETUP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Trends in atomistic simulation software usage [\versionnumber]}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% PUBLICATION INFORMATION
%%% Fill out these parameters when available
%%% These are used when the "pubversion" option is invoked
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pubDOI{10.XXXX/YYYYYYY}
\pubvolume{<volume>}
\pubissue{<issue>}
\pubyear{<year>}
\articlenum{<number>}
\datereceived{30 June 2021}
\dateaccepted{14 September 2021}

@@

\section{Author Contributions}
%%%%%%%%%%%%%%%%
% This section mustt describe the actual contributions of
% author. Since this is an electronic-only journal, there is
% no length limit when you describe the authors' contributions,
% so we recommend describing what they actually did rather than
% simply categorizing them in a small number of
% predefined roles as might be done in other journals.
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io
% for more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%%
\textbf{Leopold Talirz:} Conceptualization, Methodology, Software and Data curation for atomistic.software. Writing- Original Draft, Reviewing and Editing.\\
\textbf{Luca M. Ghiringhelli:} Conceptualization, Methodology and Data curation for the original static version of the collection. Writing- Reviewing and Editing.\\
\textbf{Berend Smit:} Supervision, Writing- Reviewing and Editing, Funding acquisition

@@

\section{Other Contributions}
%%%%%%%%%%%%%%%
% You should include all people who have filed issues that were
% accepted into the paper, or that upon discussion altered what was in the paper.
% Multiple significant contributions might mean that the contributor
% should be moved to authorship at the discretion of the a
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io for
% more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%
The authors are grateful to Nicola Marzari and Matthias Scheffler for sharing their original idea of a list of atomistic simulation codes combined with citation data. 
%Luca Ghiringhelli for being supportive of this effort to transform the static NOMAD list into an interactive application and a collaborative project.
Thanks also go to Nicola Marzari for providing the idea for table~\ref{tab:aps-most-cited} and to Kevin Jablonka for a careful reading of the manuscript.
Insightful discussions with Michele Ceriotti, Lars Holm Nielsen, Kevin Jablonka, Nicola Marzari, and Paul Saxe have contributed to the development of this work, as have numerous constructive suggestions by the anonymous reviewers of the manuscript.

@@

\section{Potentially Conflicting Interests}
%%%%%%%
%Declare any potentially competing interests, financial or otherwise
%%%%%%%
The authors declare no competing interests.
%Declare any potentially conflicting interests here, whether or not they pose an actual conflict in your view.

\section{Funding Information}
%%%%%%%
% Authors should acknowledge funding sources here. Reference specific grants.
%%%%%%%
This work was supported by the MARVEL National Centre for Competence in Research funded by the Swiss National Science Foundation (grant agreement ID~51NF40-182892), 
and the ``MaGic'' project of the European Research Council (grant agreement ID~666983).

>>>>

\usepackage{url}
\def\UrlBreaks{\do\/\do-}  %allow URLs to wrap at hyphens

@@

\newcommand{\versionnumber}{1.0}  % you should update the minor version number in preprints and major version number of submissions.
\newcommand{\githubrepository}{\url{https://github.com/ltalirz/livecoms-atomistic-software}}  %this should be the main github repository for this article

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% ARTICLE SETUP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Trends in Atomistic Simulation Software Usage [Article v\versionnumber]}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% PUBLICATION INFORMATION
%%% Fill out these parameters when available
%%% These are used when the "pubversion" option is invoked
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pubDOI{10.331/livecoms.3.1.1483}
\pubvolume{<volume>}
\pubissue{<issue>}
\pubyear{<year>}
\articlenum{<number>}
\datereceived{30 June 2021}
\dateaccepted{14 September 2021}

@@

\section*{Author Contributions}
%%%%%%%%%%%%%%%%
% This section mustt describe the actual contributions of
% author. Since this is an electronic-only journal, there is
% no length limit when you describe the authors' contributions,
% so we recommend describing what they actually did rather than
% simply categorizing them in a small number of
% predefined roles as might be done in other journals.
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io
% for more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%%
\textbf{Leopold Talirz:} Conceptualization, Methodology, Software and Data curation for atomistic.software. Writing- Original Draft, Reviewing and Editing.\\
\textbf{Luca M. Ghiringhelli:} Conceptualization, Methodology and Data curation for the original static version of the collection. Writing- Reviewing and Editing.\\
\textbf{Berend Smit:} Supervision, Writing- Reviewing and Editing, Funding acquisition

@@

\section*{Other Contributions}
%%%%%%%%%%%%%%%
% You should include all people who have filed issues that were
% accepted into the paper, or that upon discussion altered what was in the paper.
% Multiple significant contributions might mean that the contributor
% should be moved to authorship at the discretion of the a
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io for
% more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%
The authors are grateful to Nicola Marzari and Matthias Scheffler for sharing their original idea of a list of atomistic simulation codes combined with citation data. 
%Luca Ghiringhelli for being supportive of this effort to transform the static NOMAD list into an interactive application and a collaborative project.
Thanks also go to Nicola Marzari for providing the idea for table~\ref{tab:aps-most-cited} and to Kevin Jablonka for a careful reading of the manuscript.
Insightful discussions with Michele Ceriotti, Lars Holm Nielsen, Kevin Jablonka, Nicola Marzari, and Paul Saxe have contributed to the development of this work, as have numerous constructive suggestions by the anonymous reviewers of the manuscript.

@@

\section*{Potentially Conflicting Interests}
%%%%%%%
%Declare any potentially competing interests, financial or otherwise
%%%%%%%
The authors declare no competing interests.
%Declare any potentially conflicting interests here, whether or not they pose an actual conflict in your view.

\section*{Funding Information}
%%%%%%%
% Authors should acknowledge funding sources here. Reference specific grants.
%%%%%%%
This work was supported by the MARVEL National Centre for Competence in Research funded by the Swiss National Science Foundation (grant agreement ID~51NF40-182892), 
and the ``MaGic'' project of the European Research Council (grant agreement ID~666983).
